The abundance of Bullet-Groups in $\Lambda$CDM

### 2014-04-17 paper/ms.tex
Update ms.tex
version for resubmission

\title{The abundance of Bullet-Groups in $\Lambda$CDM}
\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
  G.Foex$^4$, T. Verdugo$^3$ and V. Motta$^4$} 
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\ 
       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de
  Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne,
  Besan\c{c}on, France\\ 
       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264,
  M\'erida 5101-A, Venezuela\\
  $^4$ Instituto de F\'isica y Astronom\'ia, Universidad de
  Valpara\'iso, Avda. Gran Breta\~na 1111, Playa Ancha, Valpara\'iso
  2360102, Chile  
}
\email{jfernandezt87@gmail.com}
\email{je.forero@uniandes.edu.co}
\begin{abstract}

@@

Bullet-like configurations have two dominant dark matter structures:
the host halo and the dominant sub-halo. We describe the kinematics of
this configuration by the  position and velocity vectors of the
sub-halo in a frame of reference where the main halo is at rest; thus
$\vec{v{}}=\vec{v}_{\rm sub}-\vec{v}_{\rm host}$ and
$\vec{r{}}=\vec{r}_{\rm sub}-\vec{r}_{\rm host}$, where the subscripts $host$
and $sub$ refer to the host and sub-halo, respectively. The positions
$\vec{r}$ correspond to the minimum of potential and the velocities
$\vec{v}$ are computed as an average of the bulk velocities of all
simulation particles in the structure of interest.

@@

In this Letter we work with two quantities that could be inferred
from observations of Bullet-like systems. The projected distance
between two dominant DM clumps, $d_{\rm 2D}$, and the projected distance
between the DM and the gas clumps, $d_{\rm 2D}^{\rm bar}$. The
projection is computed along the same axis for all halos at all
redshifts, we present the result of the projection along the $z$-axis
of the simulation.

@@

We thank the referee for a detailed report that improved the readability of
this Letter.

>>>>

\title{The abundance of Bullet-Groups in $\Lambda$CDM}
\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
  G.Foex$^4$, T. Verdugo$^3$ and V. Motta$^4$} 
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\ 
       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de
  Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne,
  Besan\c{c}on, France\\ 
       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264,
  M\'erida 5101-A, Venezuela\\
  $^4$ Instituto de F\'isica y Astronom\'ia, Universidad de
  Valpara\'iso, Avda. Gran Breta\~na 1111, Playa Ancha, Valpara\'iso
  2360102, Chile  
}
\email{jfernandez@obs-besancon.fr}
\email{je.forero@uniandes.edu.co}
\begin{abstract}

@@

Bullet-like configurations have two dominant dark matter structures:
the host halo and the dominant sub-halo. We describe the kinematics of
this configuration by the  position and velocity vectors of the
sub-halo in a frame of reference where the main halo is at rest; thus
$\vec{v{}}=\vec{v}_{\rm sub}-\vec{v}_{\rm host}$ and
$\vec{r{}}=\vec{r}_{\rm sub}-\vec{r}_{\rm host}$, where the subscripts $host$
and $sub$ refer to the host and sub-halo, respectively. The positions
$\vec{r}$ correspond to the minimum of potential and the velocities
$\vec{v}$ are the center of mass velocities.

@@

In this Letter we work with two quantities that could be inferred
from observations of Bullet-like systems. The projected distance
between two dominant DM clumps, $d_{\rm 2D}$, and the projected distance
between the DM and the gas clumps, $d_{\rm 2D}^{\rm bar}$. The
projection is computed along the $z$-axis for all halos at all
redshifts.

@@

We thank the referee for a detailed report that improved the clarity of
this Letter.
